## 1.3 Data reorganization

### Reading data

Each row of the file is one reaching movement.

```{r load-data}
results <- read.table("data/Results.txt", header = TRUE,
                      sep = " ", stringsAsFactors = TRUE)
names(results)
```

### Number of measures per GROUP and ID

```{r count-group-id}
results %>% count(GROUP, ID)
```

Data are missing for ID3 in the pp group, so ID3 is removed.

### Number of measures per REP

```{r count-rep}
results %>% filter(ID != "ID3") %>% count(REP)
results %>% filter(ID != "ID3") %>% count(GROUP, REP)
```

R3 is missing in the pp and ap groups, so R3 is removed.

### Clean data

```{r clean}
results_clean <- results %>%
  filter(ID != "ID3", REP != "R3") %>%
  droplevels()

# Must be balanced
results_clean %>% count(GROUP, ID, REP)
```

### Number of participants per group

```{r count-subjects}
results_clean %>%
  distinct(GROUP, SUBJ) %>%
  count(GROUP)
```

### One value per participant and ID

The ANOVA needs a single value per participant and per condition, so we average the movements.

```{r average}
data_anova <- results_clean %>%
  group_by(GROUP, SUBJ, ID) %>%
  summarise(MT = mean(MovementTime), .groups = "drop") %>%
  mutate(SUBJ = factor(SUBJ))
```

### Visualization of the interaction

```{r interaction-plot}
# Mean ± 0.5 SD, as in the assignment (mean_sdl with mult = 0.5)
mean_sd_half <- function(y) {
  data.frame(y = mean(y), ymin = mean(y) - sd(y) / 2, ymax = mean(y) + sd(y) / 2)
}

ggplot(results_clean, aes(x = ID, y = MovementTime, color = GROUP)) +
  stat_summary(fun = mean, geom = "line", aes(group = GROUP)) +
  stat_summary(fun.data = mean_sd_half, geom = "errorbar", width = 0.05) +
  stat_summary(fun = mean, geom = "point", shape = 21, fill = "white", size = 3) +
  labs(title = "Interaction between GROUP and ID on movement time",
       x = "ID", y = "Mean movement time (s)") +
  theme_minimal()
```

The lines are not parallel: movement time increases much more with ID in the pp group than in the two other groups.

### ANOVA

```{r anova}
anova_res <- ezANOVA(data = data_anova,
                     dv = MT,
                     wid = SUBJ,
                     within = ID,
                     between = GROUP,
                     detailed = FALSE)
anova_res$ANOVA
```

The effect of difficulty depends on the group: the GROUP × ID interaction is significant, F(2, 48) = 11.58, p < .001, generalized eta squared = 0.06. 
The main effects of GROUP, F(2, 48) = 37.24, p < .001, and of ID, F(1, 48) = 30.78, p < .001, are also significant.